High-speed atomic force microscopy through $\mu$-path sampling

### 2019-05-24 latex/afm-cs-main.tex
This should build.

\begin{figure}[t!]
  \centering
  \includesvg[width=1\columnwidth]{plots-afm-cs-final/figures/z_control_design.svg}
  \caption{}
  \label{fig:z_control}
\end{figure}
The entire $Z$-axis controller consists of a PI controller, $D_I(z)$ cascaded
with the resonance inversion, $D^{-1}(z)$. The inclusion of $D^{-1}$ allows us
to substantially increase the PI gain and achieve a closed-loop bandwidth of
about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}. For
comparison, the red curve in Fig.~\ref{fig:z_control} shows the closed-loop FRF
without the inverse compensator, which experiments indicate is unstable.

@@

One cause for such different gains is variation in the length of the cantilever
(and possibly how the laser was adjusted). This is illustrated in
Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
rests on the surface of some specimen with a nominal angle of $\theta$. In this
drawing, the laser is perpendicular to the sample surface. Given a vertical
perturbation $\Delta z$, we have that
\begin{equation}
  \Delta \alpha \approx \frac{d}{h} \Delta z,
\end{equation}
where $d$ is the distance from the cantilever to the detector and
$\Delta \alpha$ is the change in position of the incident laser spot on the
detector. Thus, given the same change in the vertical position, we will see a
larger change in the deflection signal for a shorter cantilever. In other words,
a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
function.
\begin{figure}
  \begin{minipage}[t]{.46\textwidth}
    % L B R T
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/z_cant_evolution.svg}
    \caption{FRFs of three different cantilevers, showing substantial
      differences in the DC-gain and smaller, but still significant differences
      the frequency of the modes.}
    \label{fig:z_evolution}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.46\textwidth}
    % L B R T
    \includegraphics[width=1\textwidth]{plots-afm-cs-final/figures/z_axis_gain_schematic-crop.pdf}
    \caption{Schematic drawing of how the length of the cantilever affects the
      $z$-axis gain.}
    \label{fig:z_axis_gain}
  \end{minipage}
\end{figure}

@@

Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
$D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
will get a lot of wiggles in the resulting signal. Rather, we need to take only
the output of the integrator to represent the surface.
% \begin{figure}
%   \centering
%   \includegraphics[width=1\columnwidth]{plots-afm-cs-final/figures/AFM_loop_Dinv-crop.pdf}
%   \caption{Block diagram of the $Z$-axis control loop with the inverse
%   compensator. }
%   \label{fig:afm_bd_dinv}
% \end{figure}
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.75\textwidth]{plots-afm-cs-final/figures/AFM_loop_Dinv_antiwup-crop.pdf}
  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
    for decision index $i\in\{0,1,5\}$, which correspond to states such that
    $r_Z=r_{Z,\textrm{up}}$.}
  \label{fig:afm_bd_dinv_final}
\end{figure*}

@@

% Several cycles of the CS-scheme are shown in
% Fig.~\ref{fig:mupathsignaltrajectory}. Each of these differences is discussed
% more fully in the following three subsections.
\begin{figure*}[ht!]
  \centering \includesvg[scale=0.85]{plots-afm-cs-final/figures/cs_cycle.svg}
  \caption{Several CS cycles. Each state is indicated by color.}
  \label{fig:mupathsignaltrajectory}
\end{figure*}

% \begin{figure*}
%   \centering
%   \includesvg[width=.9\textwidth]{plots-afm-cs-final/figures/state-machine-final.svg}
%   \caption{Diagram of the state-machine implemented in the final design.}
%   \label{fig:sm_final}
% \end{figure*}

@@

\begin{figure}[ht!]
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/justify_small_lift.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=01\textwidth]{plots-afm-cs-final/figures/justify_small_lift_zoom.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \caption{One CS-cycle with different dis-engagement heights. (a) Full view.
    (b) Zoomed-in view. Note the drift transient in the left panel of (b). }
  \label{fig:z_drift}
\end{figure}

@@

\subsection{The pre-scan}
\begin{figure*}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/zbounce_uz_example.svg}
    \caption{ }
    \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/prescan_uz_example.svg}
    \caption{ }
    \label{fig:uz_prescan}
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/prescan_zbounce_PSD.svg}
    \caption{ }
    \label{fig: }
  \end{subfigure}
  \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless
    and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a
    tightly packed set of CS-cycles where the movement between each measurement
    location is 0. (c) PSDs from the portions of the trajectories which are
    colored blue and turquoise, averaged over many such cycles, demonstrating
    that the scan process itself reduces vibration in the $Z$-axis.}
  \label{fig:prescan_difference}
\end{figure*}
After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)). To
motivate, this consider Fig.~\ref{fig:prescan_difference}. The left panel
represents what we call a ``$Z$''-bounce experiment, where the $XY$-stage stays
motionless, but we repeatedly retract and re-engage the tip with specimen,
exactly as we would in a CS scan. The right panel represents a single cycle from
specialized CS pattern, where the $\mu$-paths are still 500 nm long, but the
paths are separated by 0 pixels. In this case, the specimen is freshly cleaved
mica. The goal here is to eliminate (i) any oscillations which arise from the
$XY$-move (which, as we will show in Section ~\ref{sec:need_mimo}, can be
significant) and (ii) to have a perfectly flat surface to scan over so that
there are as few disturbances as possible entering the control loop. Finally,
the middle panel of Fig.~\ref{fig:prescan_difference} shows the PSDs of the left
and right panels (but averaged over many similar cycles). Note that the PSD is
only computed from the combination of the blue and turquoise signals.

@@

\section{A New Metric}\label{sec:rdi}
\begin{figure}[t!]
  \centering
  \includesvg[width=1\columnwidth]{plots-afm-cs-final/figures/damage_illustration.svg}
  \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes everything in the
    red shaded region and does not penalize anything in the un-shaded region.}
  \label{fig:damage_illustrate}
\end{figure}
In Chapter~\ref{chap:cs_init} that we employed two metrics, the SSIM and PSNR,
to compare different raster and CS scans to a master image. We took the master
image as a raster scan taken at a slow rate. These metrics only assess the
similarity of two images. However, in AFM imaging, pure image quality is not the
only concern, particularly for delicate samples. What is needed is a figure of
merit for how much damage was done to specimen during the imaging process. While
this is not really a concern while imaging a hard calibration grating, it plays
a prominent role biological samples~\cite{ando_highspeed_2008}. In general,
damage occurs while scanning into an uphill region, which results in a positive
deflection signal. The actual damage done by a given $Z_d$ will depend on the
spring constant of the cantilever and the softness of the specimen. Nonetheless,
we can use the positive deviations of $Z_d$ as a relative measure of damage
between different scan speeds or scanning methods, for a given cantiliver and
specimen. This motivates a metric we term the relative damage index (RDI), which
we define as
\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
  I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
\end{align}
where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the
deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint.
The RDI is basically the power in positive deflection. By excluding negative
values of the deflection, we do not penalize the CS algorithm while it is
re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint,
which we do want to penalize. This is illustrated in
Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly
tuned controller. Only deflection signals in the red-shaded region will be
penalized by the RDI.

@@

\begin{figure}[t!]
  % ------------ 1.0 Hz ---------------------
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_noalign_1Hz.svg}
    \caption{1.0~Hz, no alignment.}
    \label{fig:rast_unaligned_1}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_aligned_1Hz.svg}
    \caption{1.0~Hz, with alignment.}
    \label{fig:rast_aligned_1}
  \end{subfigure}
% 
  \caption{Errors between a ''master'' and 6 different raster scans, all taken
    sequentially and at a scan rate of 0.5 Hz. (a) Errors without alignment (b)
    The same data as above in (a) but aligned via cross correlation.}
  \label{fig:baseline_errors}
\end{figure}

@@

\begin{figure*}
  \includesvg[scale=1]{plots-afm-cs-final/figures/cs_raster_images_4-26-2019}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
    indicated by the red line are shown in \ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

% \begin{figure*}
%   \includesvg[scale=1]{plots-afm-cs-final/figures/cs_raster_images_err_4-26-2019}
%   \caption{Errors between aligned sub-slices of the 1.0~Hz raster image and
%   the remaining scans. The original scans are shown in
%   Fig.~\ref{fig:resultsF1_images}.}
%   \label{fig:resultsF1_errs}
% \end{figure*}

\begin{table}[t!]
  \centering
  \caption{Performance metrics for the scans taken on 4-26-2019. All CS images
    filtered with TV denoising, $\mu$=100.}
  \begin{tabular}{cccccc}
    \input{plots-afm-cs-final/tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
  \label{tab:rast_vs_cs_v1}
\end{table}

\begin{table}[t!]
  \centering
  \caption{Breakdown of state times for the CS scans listed in
    Table~\ref{tab:rast_vs_cs_v1}. All times are in seconds.}
  \label{tab:final_state_times}
  \begin{tabular}{ccccccc}
    \input{plots-afm-cs-final/tables/cs_state_times_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
\end{table}

\begin{figure*}[t!]
  \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/cs_raster_pixel_rows_3-20-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure*}

@@

\begin{figure*}[t!]
  \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_rast_time_vs_ssim_psnr.svg}
    \caption{(left) SSIM as a function of total acquisition time. (right) PSNR
      as a function of total acquisition time.}
    \label{fig:time_ssim_psnr}
  \end{subfigure}

  \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_rast_damage.svg}
    \caption{(left) RDI as a function of scan rate for raster scans and CS scans
      at 10\% and 15\% sampling. (right) RDI as a function of total imaging
      time.}
    \label{fig:time_damage}
  \end{subfigure}

>>>>

\begin{figure}[t!]
  \centering
  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
  \caption{}
  \label{fig:z_control}
\end{figure}
The entire $Z$-axis controller consists of a PI controller, $D_I(z)$ cascaded
with the resonance inversion, $D^{-1}(z)$. The inclusion of $D^{-1}$ allows us
to substantially increase the PI gain and achieve a closed-loop bandwidth of
about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}. For
comparison, the red curve in Fig.~\ref{fig:z_control} shows the closed-loop FRF
without the inverse compensator, which experiments indicate is unstable.

@@

One cause for such different gains is variation in the length of the cantilever
(and possibly how the laser was adjusted). This is illustrated in
Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
rests on the surface of some specimen with a nominal angle of $\theta$. In this
drawing, the laser is perpendicular to the sample surface. Given a vertical
perturbation $\Delta z$, we have that
\begin{equation}
  \Delta \alpha \approx \frac{d}{h} \Delta z,
\end{equation}
where $d$ is the distance from the cantilever to the detector and
$\Delta \alpha$ is the change in position of the incident laser spot on the
detector. Thus, given the same change in the vertical position, we will see a
larger change in the deflection signal for a shorter cantilever. In other words,
a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
function.
\begin{figure}
  \begin{minipage}[t]{.46\textwidth}
    % L B R T
    \includesvg[width=1\textwidth]{figures/z_cant_evolution.svg}
    \caption{FRFs of three different cantilevers, showing substantial
      differences in the DC-gain and smaller, but still significant differences
      the frequency of the modes.}
    \label{fig:z_evolution}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.46\textwidth}
    % L B R T
    \includegraphics[width=1\textwidth]{figures/z_axis_gain_schematic-crop.pdf}
    \caption{Schematic drawing of how the length of the cantilever affects the
      $z$-axis gain.}
    \label{fig:z_axis_gain}
  \end{minipage}
\end{figure}

@@

Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
$D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
will get a lot of wiggles in the resulting signal. Rather, we need to take only
the output of the integrator to represent the surface.
% \begin{figure}
%   \centering
%   \includegraphics[width=1\columnwidth]{figures/AFM_loop_Dinv-crop.pdf}
%   \caption{Block diagram of the $Z$-axis control loop with the inverse
%   compensator. }
%   \label{fig:afm_bd_dinv}
% \end{figure}
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
    for decision index $i\in\{0,1,5\}$, which correspond to states such that
    $r_Z=r_{Z,\textrm{up}}$.}
  \label{fig:afm_bd_dinv_final}
\end{figure*}

@@

% Several cycles of the CS-scheme are shown in
% Fig.~\ref{fig:mupathsignaltrajectory}. Each of these differences is discussed
% more fully in the following three subsections.
\begin{figure*}[ht!]
  \centering \includesvg[scale=0.85]{figures/cs_cycle.svg}
  \caption{Several CS cycles. Each state is indicated by color.}
  \label{fig:mupathsignaltrajectory}
\end{figure*}

% \begin{figure*}
%   \centering
%   \includesvg[width=.9\textwidth]{figures/state-machine-final.svg}
%   \caption{Diagram of the state-machine implemented in the final design.}
%   \label{fig:sm_final}
% \end{figure*}

@@

\begin{figure}[ht!]
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{figures/justify_small_lift.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=01\textwidth]{figures/justify_small_lift_zoom.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \caption{One CS-cycle with different dis-engagement heights. (a) Full view.
    (b) Zoomed-in view. Note the drift transient in the left panel of (b). }
  \label{fig:z_drift}
\end{figure}

@@

\subsection{The pre-scan}
\begin{figure*}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{figures/zbounce_uz_example.svg}
    \caption{ }
    \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{figures/prescan_uz_example.svg}
    \caption{ }
    \label{fig:uz_prescan}
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{figures/prescan_zbounce_PSD.svg}
    \caption{ }
    \label{fig: }
  \end{subfigure}
  \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless
    and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a
    tightly packed set of CS-cycles where the movement between each measurement
    location is 0. (c) PSDs from the portions of the trajectories which are
    colored blue and turquoise, averaged over many such cycles, demonstrating
    that the scan process itself reduces vibration in the $Z$-axis.}
  \label{fig:prescan_difference}
\end{figure*}
After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)). To
motivate, this consider Fig.~\ref{fig:prescan_difference}. The left panel
represents what we call a ``$Z$''-bounce experiment, where the $XY$-stage stays
motionless, but we repeatedly retract and re-engage the tip with specimen,
exactly as we would in a CS scan. The right panel represents a single cycle from
specialized CS pattern, where the $\mu$-paths are still 500 nm long, but the
paths are separated by 0 pixels. In this case, the specimen is freshly cleaved
mica. The goal here is to eliminate (i) any oscillations which arise from the
$XY$-move (which, as we will show in Section ~\ref{sec:need_mimo}, can be
significant) and (ii) to have a perfectly flat surface to scan over so that
there are as few disturbances as possible entering the control loop. Finally,
the middle panel of Fig.~\ref{fig:prescan_difference} shows the PSDs of the left
and right panels (but averaged over many similar cycles). Note that the PSD is
only computed from the combination of the blue and turquoise signals.

@@

\section{A New Metric}\label{sec:rdi}
\begin{figure}[t!]
  \centering
  \includesvg[width=1\columnwidth]{figures/damage_illustration.svg}
  \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes everything in the
    red shaded region and does not penalize anything in the un-shaded region.}
  \label{fig:damage_illustrate}
\end{figure}
In Chapter~\ref{chap:cs_init} that we employed two metrics, the SSIM and PSNR,
to compare different raster and CS scans to a master image. We took the master
image as a raster scan taken at a slow rate. These metrics only assess the
similarity of two images. However, in AFM imaging, pure image quality is not the
only concern, particularly for delicate samples. What is needed is a figure of
merit for how much damage was done to specimen during the imaging process. While
this is not really a concern while imaging a hard calibration grating, it plays
a prominent role biological samples~\cite{ando_highspeed_2008}. In general,
damage occurs while scanning into an uphill region, which results in a positive
deflection signal. The actual damage done by a given $Z_d$ will depend on the
spring constant of the cantilever and the softness of the specimen. Nonetheless,
we can use the positive deviations of $Z_d$ as a relative measure of damage
between different scan speeds or scanning methods, for a given cantiliver and
specimen. This motivates a metric we term the relative damage index (RDI), which
we define as
\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
  I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
\end{align}
where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the
deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint.
The RDI is basically the power in positive deflection. By excluding negative
values of the deflection, we do not penalize the CS algorithm while it is
re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint,
which we do want to penalize. This is illustrated in
Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly
tuned controller. Only deflection signals in the red-shaded region will be
penalized by the RDI.

@@

\begin{figure}[t!]
  % ------------ 1.0 Hz ---------------------
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{figures/baseline_errors_noalign_1Hz.svg}
    \caption{1.0~Hz, no alignment.}
    \label{fig:rast_unaligned_1}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{figures/baseline_errors_aligned_1Hz.svg}
    \caption{1.0~Hz, with alignment.}
    \label{fig:rast_aligned_1}
  \end{subfigure}
% 
  \caption{Errors between a ''master'' and 6 different raster scans, all taken
    sequentially and at a scan rate of 0.5 Hz. (a) Errors without alignment (b)
    The same data as above in (a) but aligned via cross correlation.}
  \label{fig:baseline_errors}
\end{figure}

@@

\begin{figure*}
  \includesvg[scale=1]{figures/cs_raster_images_4-26-2019}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
    indicated by the red line are shown in \ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

% \begin{figure*}
%   \includesvg[scale=1]{figures/cs_raster_images_err_4-26-2019}
%   \caption{Errors between aligned sub-slices of the 1.0~Hz raster image and
%   the remaining scans. The original scans are shown in
%   Fig.~\ref{fig:resultsF1_images}.}
%   \label{fig:resultsF1_errs}
% \end{figure*}

\begin{table}[t!]
  \centering
  \caption{Performance metrics for the scans taken on 4-26-2019. All CS images
    filtered with TV denoising, $\mu$=100.}
  \begin{tabular}{cccccc}
    \input{tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
  \label{tab:rast_vs_cs_v1}
\end{table}

\begin{table}[t!]
  \centering
  \caption{Breakdown of state times for the CS scans listed in
    Table~\ref{tab:rast_vs_cs_v1}. All times are in seconds.}
  \label{tab:final_state_times}
  \begin{tabular}{ccccccc}
    \input{tables/cs_state_times_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
\end{table}

\begin{figure*}[t!]
  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_3-20-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure*}

@@

\begin{figure*}[t!]
  \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{figures/cs_rast_time_vs_ssim_psnr.svg}
    \caption{(left) SSIM as a function of total acquisition time. (right) PSNR
      as a function of total acquisition time.}
    \label{fig:time_ssim_psnr}
  \end{subfigure}

  \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{figures/cs_rast_damage.svg}
    \caption{(left) RDI as a function of scan rate for raster scans and CS scans
      at 10\% and 15\% sampling. (right) RDI as a function of total imaging
      time.}
    \label{fig:time_damage}
  \end{subfigure}
